Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-08-30 doc/paper.tex
LS pseudocode added

      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$. Afterwords, for each $p_i$ which are dropped off, we take the guard which is nearest by distance from $p_i$ and add them into $s^p$. 
     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$. 
       	  \item \emph{topological-type benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price. 
       	  \item    ...
       \end{itemize}
     \section{Conclusions and Future Work}

>>>>

      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$. Afterwords, for each $p_i$ which are dropped off, we take the guard which is nearest by distance from $p_i$ and add them into $s^p$.

       \begin{algorithm}[!t] 
      	\caption{Local Search}\label{alg:local-search}
      	\begin{algorithmic}[1]
      		\State \textbf{Input:} a (partial) solution $s_{greedy}=\{v_1,...,v_k\}$, $iter_{allow}>0.$
      		\State \textbf{Output:} and improved solution $s$
      		\While{$iter < iter_{allow}$}
      		     \State $D(P)_s$ the number of points covered by $s_{greedy}$
      		      \If{$|D(P)_s| == |D(P)|$} // a complete solution 
      		          \State return $s_{greedy}$
      		      \EndIf
      		     \State choose random vertex $v_{i'}$ from $s_{greedy}$
      		     \State $v_{i''} \gets$ consider neighbor vertices of vertex  $v_{i'}$ (two are possible) and choose one of them
      		     \State $s^1_{greedy} \gets$ $s_{greedy} \cup \{v_{i''} \} \setminus \{v_{i'}\}$
      		      \If{$s_{greedy}$ do not improve  $D(P)_s$}
      		           \State $v_{i'''} \gets$ take the second neighbor vertex of $v_{i'}$
      		           \State $s^2_{greedy} \gets$ swap $v_{i'''}$ with  $v_{v'}$ in  $s_{greedy}$
      		           \If{$s^2_{greedy}$ do not improve $D(P)_s$}
      		                  \If{$s^1_{greedy} \vee s^2_{greedy}$ cover the same number of points as $D(P)_s$}
      		                     \State with random probability  0.5, choose the right for a new $s_{greedy}$
      		                \Else

      		                     \State \emph{goto} line 4
      		                \EndIf
      		           \EndIf
      		      \EndIf

      		     \State $iter \gets iter +1 $
      		\EndWhile
      	\end{algorithmic}
      \end{algorithm}

     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$. 
       	  \item \emph{topological-type benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price. 
       	  \item    ...
       \end{itemize}
     \section{Conclusions and Future Work}
